Teaching a Class to Grade Itself using Game Theory

### 2013-09-19 Primes Write up.tex
Added conclusion and project abstract, all thats left are illustrations and edits

\section{Illustrations}
{
\noindent
\includegraphics[width=\textwidth]{Chart.eps}
}
\bibliography{bibliography}{}
\bibliographystyle{plain}
\end{document}

>>>>

\section{Illustrations}
{
\noindent
\includegraphics[width=\textwidth]{Chart.eps}
}
\section{Conclusion}
In this research, we learned and established the validity of game theory and matematically based models when solving complex problems involving human nature. Using this to answer the unanswered of how professors should go about grading the astronomically high number of papers submitted by students in the online courses known as MOOCs

Theoretically, all of our results are perfectly valid, however one must acknowledge that theory is not practice. Because of this, it becomes hard to say how valid our results are, since they have not been tested in the real world. In the real world, there is always the chance that theory falls apart; this is the main flaw in the validity of our results.

Also, the only other flaw, which is minor in comparison, is that the mechanisms do not account for a perfectly realistic world. Even though we completed a model which can be built upon, and applies to the real world, the mechansims designed around this model do not address the real world, since they lack the capacity to account for students who are incapable of grading well.

Although there are some errors in the validity of our results, all of them were established and created independant of any prior literature. One of the main advantages of this research is that it has not been done before; this is what makes it an interesting idea to explore and develop upon. Because of this, there is no prior literature that addresses the problem at hand in the same way that we do.

In the future, one of the experiments that would truly confirm the validity of our results would be to test them in the real world. With real world testing in a system where assignments need to be graded, it would quickly become apparent whether the theory behind our mechanisms actually works, and how well it works in the real world. This would fix the first of the validity errors that the mechanisms have.

To address the second of these validity errors, more work would need to be done to make the models realistic. If we had more time, this would be the first thing that we would do; creating a mechanism that applies to a more realistic world would ready the theory for real testing, and would also patch the second hole in the validity of the mechanisms.

After finalizing the mechanisms, our preffered next step would be to implement software in an existing course system, and use it to test out our ideas. By implementing this, it would allow us to use what already exists and build upon it. This means that not much would have to be done to encourage people to use it, since they would already be using whatever we implemented it on. Also, this would allow us to receive real data for the theory, and using this we could continue the improvement cycle.

Even though the mechansims are not truly valid, only one true question remains unanswered. This question being the question of what happens when our theory is introduced into the real world. As stated previously, to solve this question, we would prefer to create a system of implementation that would allows us to test our mechanisms.
\bibliography{bibliography}{}
\bibliographystyle{plain}
\end{document}
